Matching Bullets

### 2015-11-23 imaging-paper.Rnw
teensy comments

For this, assume that $n$ data points $(x_1, y_1), (x_2, y_2), ..., (x_n, y_n)$ are given that are (approximately) located on a circle. We want to estimate the location of the center and radius of the best fitting circle using a least squares approach.

@@

The scatterplot in Figure~\ref{fig:residual} shows the residuals of such a fit. The residuals are dominated, as expected, by the grooves, which show up as large positive residuals. For a surface cross cut at $x = 100$ there is a residual circular structure that does not show up for all cross sections.

>>>>

For this, assume that $n$ data points are given in form of data tuples $(x_1, y_1), (x_2, y_2), ..., (x_n, y_n)$ that are (approximately) located on a circle. We want to estimate the location of the center and radius of the best fitting circle using a least squares approach.

@@

\hh{XXX add parameter estimates? $\hat{r} \approx 4500$ - indicating a 9 mm bullet, amount of degrees covered by land?  }
The scatterplot in Figure~\ref{fig:residual} shows the residuals of such a fit. The residuals are dominated, as expected, by the grooves, which show up as large positive residuals. For a surface cross cut at $x = 100$ there is a residual circular structure that does not show up for all cross sections.
